\bf $\mathsf{TEDAT}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-19 paper.tex
more on Bandwidth Availability

\textbf{High availability directly translates into profit.}
Nowadays, high availability is nearly always one of the main items in SLAs  \cite{amazon,azure,amazon2}, and customers are eligible for a credit refund  if there are SLA violations. 
We conduct a survey on the SLA claims of different cloud providers, and Table \ref{target} shows their declared availability targets and  corresponding refunding policies,
%when violated.
%We can see that service providers often use a progressive piecewise function to derive refunding credits for violating availability targets. 
where the refunding credit is typically represented by a simple step function. 
For example, Microsoft Azure provides 10\% refund if its Traffic Manager service availability falls between 99.99\% and
99.0\%, and provides 30\% refund for anything below 99.0\% availability \cite{azure}. As more realtime and mission-critical applications (financial trading, online game, video streaming,
instant messaging, live broadcast, etc.) are deployed on the Internet, providing hard guarantee of high service availability under network failures to retain a good profit is a big challenge.

>>>>

\textbf{High availability directly translates into profit.}
Nowadays, high availability is nearly always one of the main items in SLAs  \cite{amazon,azure,amazon2}, and customers are eligible for a credit refund  if there are SLA violations. 
We conduct a survey on the SLA claims of different cloud providers, and Table \ref{target} shows their declared availability targets and  corresponding refunding policies,
%when violated.
%We can see that service providers often use a progressive piecewise function to derive refunding credits for violating availability targets. 
where the refunding credit is typically represented by a simple step function. 
For example, Microsoft Azure provides 10\% refund if its Traffic Manager service availability falls between 99.99\% and
99.0\%, and provides 30\% refund for anything below 99.0\% availability \cite{azure}. As more realtime and mission-critical applications (financial trading, online game, video streaming,
instant messaging, live broadcast, etc.) are deployed on the Internet, \textit{providing hard guarantee of high service availability under network failures to retain a good profit is a big challenge}.
